%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Wenneker Resume/CV
% LaTeX Template

% Original author:
% Frits Wenneker (http://www.howtotex.com) with extensive modifications by 
% Vel (vel@LaTeXTemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[a4paper,12pt]{article} % Font and paper size
\newcommand{\CVSection}[1]{ % New command for the headings within sections
{\Large\textbf{#1}}\par
\SmallSep % Used for spacing
}

\setlength{\parskip}{0.5em}

\begin{document}

\begin{large}
\noindent	\textbf{Cover Letter}
\end{large}

\noindent Dear Sir/Madam,

I am Enoch Yi-Tung Chen. I am thrilled to see your posting for the position of research assistant in Biostatistics. I am positive that I can help with the development in evidence-based health policy decision system for both Sweden and Taiwan.

I graduated with a master's degree in Epidemiology from Karolinska Institutet in 2020 and a bachelor's degree in Public Health from National Taiwan University in 2018. I am fluent in both Mandarin Chinese, my mother tongue, and English, my first foreign language.

Currently, I am a research assistant at the Biostatistics group at the Department of Medical Epidemiology and Biostatistics, Karolinska Institutet. Last year, I worked as a summer intern in National Cheng Kung University using iSQoL package
with Taiwan's National Healthcare Database simulation data to analyse cost-effectiveness studies.

In my past thesis work during my master's studies, I completed my thesis in comparing between two different models of survival extrapolation, including rolling-over algorithm and the flexible parametric model. I used data from the Swedish Cancer Register to extrapolate cancer patients' survival using R and
Stata. Apart from my thesis work, I also worked as a part-time intern in a health information
consulting company called Synergus Real World Evidence for six months. I was focused on the generalisability assessment of stroke healthcare delivery in Sweden by conducting literature reviews and comparing data with other EU countries.

From previous experience in both academia and industries, I was inspired to understand that a successful estimate of survival, health benefits or burden can help us quantify the societal impact of disease on both the individual and the population level. A further step of my current study in survival extrapolation is to conduct cost-effectiveness studies in health technology assessment, which is a perfect match for my personal interest and the target of this proposed project.

Working as a research assistant in Biostatistics is a precious opportunity to me. I would love to dedicate myself to the work again to this job. I am convinced that I meet the expectations of this job. I hope to be given this job, as I am also confident that I will be a valuable assistant in the team.

Kind Regards, \\
\indent Enoch Yi-Tung Chen

\end{document}
